Experimentally informed site-specific substitution models deepen phylogenetic estimates of the divergence of viral lineages

### 2018-02-14 manuscript/manuscript.tex
tweaks to decay and simulations figure legends

\begin{figure}[H]
\centerline{\includegraphics[width=0.90\textwidth]{figures/decay.pdf}}
\caption{\label{fig:decay}
\textbf{Effect of stationary state and rate variation on long branch estimation.}
The expected pairwise amino-acid identity for five sites in influenza hemagglutinin (HA) for four different substitution models calculated using \ref{eq:f}. 
The logoplots show the HA amino-acid preferences from a deep mutational scan performed by \cite{doud2016accurate}. 
The implied dN/dS value was calculated from the ExpCM following \cite{spielman2015relationship} (\ref{eq:w_r}).
\skhcomment{ Maybe change long branch length to expected asymptotic sequence divergence.}
}
\end{figure}

@@

\begin{figure}[H]
\centerline{\includegraphics[width=0.85\textwidth]{figures/simulations}}
\caption{\label{fig:simulations}
\textbf{Model performance under simulated, site-specific data.} 
Alignments were simulated under an ExpCM along an HA tree and the branches were re-optimized by a model from the ExpCM or YNGKP family. 
The averaged ExpCMs amino-acid frequencies defined by the average preference of that amino acid across all sites in the protein. 
While these models extract information from the deep mutational scanning experiment, they are not site-specific. 
Grey points represent the length of one branch and the black points are the mean branch lengths over ten simulations. 
The grey, dashed line is the reference line $y=x$, depicting the behavior of a model which is an unbiased estimator of the simulated branch length. 
}
\end{figure}

>>>>

\begin{figure}[H]
\centerline{\includegraphics[width=0.90\textwidth]{figures/decay.pdf}}
\caption{\label{fig:decay}
\textbf{Effect of stationary state and $\Gamma\omega$ rate variation on expected asymptotic sequence divergence.}
For each model, the expected amino-acid identity given some branch length is calculated using \ref{eq:f}. 
The deep mutational scanning amino-acid preferences from \cite{doud2016accurate} defining the ExpCM (red) are shown as logoplots. 
The implied dN/dS ($\omega_r$) for the GY94+$\omega_r$ (yellow) is calculated from the ExpCM using \ref{eq:w_r}. 
\skhcomment{I use `implied dN/dS' to refer to two different concepts in the results.}
}
\end{figure}

@@

\begin{figure}[H]
\centerline{\includegraphics[width=0.85\textwidth]{figures/simulations}}
\caption{\label{fig:simulations}
\textbf{Model performance under simulated, site-specific data.} 
Alignments were simulated under an ExpCM and branch lengths were re-estimated using models from the ExpCM and GY94 families. 
The averaged ExpCMs have a uniform stationary state defined by the average preference for each amino acid across all sites in the protein. 
The length of one branch in one simulation is shown in grey and the average branch length of one branch across ten simulations is shown in black. 
The grey, dashed line is the reference line $y=x$, representing the behavior of an unbiased estimator. 
}
\end{figure}
